### 2022-06-15 sections/awards.tex
Update awards.tex
LPPL v1.3c

\cvsection{Honours \& Awards}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Travel Grant} 
{Allowances for conference participation in the USA, {\pounds} 950} 
{Oxford, UK}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Book Grant} 
{Research grant for the training of machine learning algorithms, DPhil (PhD) project data storage, and allowances for books, {\pounds} 530} 
{Oxford, UK}
{2021}
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{St Hilda's College Travel and Book Grants} 
{Allowances for conference participation in Portugal and books, {\pounds} 745} 
{Oxford, UK}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{LASA Travel Grant} 
{Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
{New York, USA}
{2016}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{CESS Summer School Scholarship}
{Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
{Santiago, Chile}
{2016}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{ALACIP Methodological School Prize}
{Best methodological work at the Latin American Political Association School (ALACIP)}
{Lima, Peru}
{2015}
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{ACCP Winter School Scholarship}
{Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association (ACCP), {\pounds} 300}
{Montevideo, URY}
{ 2015}
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{PUC Summer School Scholarship}
{Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
{Santiago, Chile}
{2014} 
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{Comunicracia Prize}
{Best paper of the political communication area at the XI Argentinian Congress of Political Science (double-blind peer-review), {\pounds} 170}
{Parana, Argentina}
{2013}
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{Highest Rating MA Dissertation}
{The highest rating and the congratulations from the jury at the Universidad de Chile}
{Santiago, Chile}
{2013}
\end{cvhonors}

>>>>

\cvsection{Relevant Honours \& Awards}

@@

\begin{cvhonors}
\cvhonor
{SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1,400}
{Bath, UK}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
{Research support grant for my DPhil (PhD) project and allowance for participation in conferences and purchase of books, {\pounds} 2,225} 
{Oxford, UK}
{2022}
\end{cvhonors}

@@

%% \begin{cvhonors}
%% \cvhonor
%% {LASA Travel Grant} 
%% {Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
%% {New York, USA}
%% {2016}
%% \end{cvhonors}

%% \vspace{1mm}

%% \begin{cvhonors}
%% \cvhonor
%% {CESS Summer School Scholarship}
%% {Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences (CESS), {\pounds} 200}
%% {Santiago, Chile}
%% {2016}
%% \end{cvhonors}

%% \vspace{1mm}

\begin{cvhonors}
\cvhonor
{ALACIP Methodological School Prize}
{Best methodological work at the Latin American Political Association (ALACIP) School}
{Lima, Peru}
{2015}
\end{cvhonors}

@@

%% \begin{cvhonors}
%% \cvhonor
%% {ACCP Winter School Scholarship}
%% {Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association (ACCP), {\pounds} 300}
%% {Montevideo, URY}
%% { 2015}
%% \end{cvhonors}

%% \vspace{1mm}

%% \begin{cvhonors}
%% \cvhonor
%% {PUC Summer School Scholarship}
%% {Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile (PUC), {\pounds} 170}
%% {Santiago, Chile}
%% {2014} 
%% \end{cvhonors}

%% \vspace{1mm}

\begin{cvhonors}
\cvhonor
{Comunicracia Prize}
{Best paper of the political communication area at the XI Argentine Congress of Political Science (double-blind peer-review)} %% {\pounds} 170
{Parana, Argentina}
{2013}
\end{cvhonors}

@@

%% \begin{cvhonors}
%% \cvhonor
%% {Highest Rating MA Dissertation}
%% {The highest rating and the congratulations from the jury at the Universidad de Chile}
%% {Santiago, Chile}
%% {2013}
%% \end{cvhonors}

%% \vspace{1mm}
